---
title: "Design Efficiency"
format: html
theme: united
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.path = "figs/",
    fig.width = 7.252,
    fig.height = 4,
    comment = "#>",
    fig.retina = 3
)

library(tidyverse)
library(cbcTools)
```

# Measuring D-efficiency of experiment designs

Make a simple design of experiment for a conjoint survey on apples

First, define the attributes and levels:

```{r}
profiles <- cbc_profiles(
    type = c("Implantable", "Ring", "Bracelet", "Card"),
    price = c(25, 50, 100),
    compatibility = c("iOS", "Android", "iOS/Android"),
    capacity = c(1,3,5), #No of cards
    range = c(0.1,0.5,1) #feet
)
```

Make a randomized full-factorial design:

```{r}
design_rand <- cbc_design(
  profiles = profiles,
  n_resp   = 500, # Number of respondents
  n_alts   = 3,   # Number of alternatives per question
  n_q      = 6    # Number of questions per respondent
)

head(design_rand)

cbc_inspect(design_rand)
```

Make a Bayesian D-efficient fractional factorial design:

```{r}
priors = cbc_priors(
    profiles,
    type       = c(1,1,2),
    price = -0.1,
    compatibility   = c(-1,1),
    capacity  = 1,
    range     = 1
)

design_db_eff <- cbc_design(
  profiles  = profiles,
  n_resp    = 500, # Number of respondents
  n_alts    = 3, # Number of alternatives per question
  n_q       = 6, # Number of questions per respondent
  n_start   = 5, 
  n_blocks  = 1,
  priors = priors,
  method = "modfed"
)

head(design_db_eff)

cbc_inspect(design_db_eff)
```

Tuning Parameters:

- `n_start`: Number of random starts when searching for D-efficient design.
- `n_blocks`: Number of blocks used for D-efficient design. More blocks increases overall efficiency (more people see more different questions), but increases computation time to create design.
- Change `method` to `"modfed"`: Use the modified Federov algorithm instead of `"cea"`.
