---
  title: "Power Analysis"
format: html
theme: united
---

  ```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

library(tidyverse)
library(cbcTools)
```

First, define the attributes and levels:

  ```{r}
profiles <- cbc_profiles(
  price       = c(15, 20, 25), # Price ($1,000)
  fuelEconomy = c(20, 25, 30), # Fuel economy (mpg)
  accelTime   = c(6, 7, 8),    # 0-60 mph acceleration time (s)
  powertrain  = c('Gasoline', 'Electric')
)
```

# Random design

Make a randomized full-factorial design:

  ```{r}
design_rand <- cbc_design(
  profiles = profiles,
  n_resp   = 500, # Number of respondents
  n_alts   = 3,   # Number of alternatives per question
  n_q      = 6    # Number of questions per respondent
)

head(design_rand)

cbc_inspect(design_rand)
```

Simulate random choices

```{r}
priors <- cbc_priors(
  profiles,
  price       = -0.1,
  fuelEconomy = 0.1,
  accelTime   = -0.1,
  powertrain  = -4
)

choices_rand <- cbc_choices(
  design = design_rand,
  priors = priors
)
```

Run power analysis

```{r}
power_rand <- cbc_power(
  data = choices_rand,
  outcome = "choice",
  obsID = "obsID",
  n_q = 6,
  n_breaks = 10,
  pars    = c("price", "fuelEconomy", "accelTime", "powertrain")
)

power_rand
```

Here is a summary of the standard errors for each sample size:

  ```{r}
plot(
  power_rand,
  type = "power"
)

plot(
  power_rand,
  type = "se"
)
```



# Bayesian D-efficient design

Make a Bayesian D-efficient fractional factorial design:

  ```{r}
priors <- cbc_priors(
  profiles,
  price       = -0.1,
  fuelEconomy = 0.1,
  accelTime   = -0.1,
  powertrain  = -4
)

design_db_eff <- cbc_design(
  profiles  = profiles,
  n_resp    = 500, # Number of respondents
  n_alts    = 3,   # Number of alternatives per question
  n_q       = 6,   # Number of questions per respondent
  n_start   = 10,
  n_blocks  = 1,
  priors = priors,
  method = 'modfed'
)

cbc_inspect(design_db_eff)
```

Simulate choices

```{r}
choices_db_eff <- cbc_choices(
  design = design_db_eff,
  priors = priors
)
```

Run power analysis

```{r}
power_db_eff <- cbc_power(
  data = choices_db_eff,
  outcome = "choice",
  obsID = "obsID",
  n_q = 6,
  n_breaks = 10,
  pars    = c("price", "fuelEconomy", "accelTime", "powertrain")
)

power_db_eff
```

Here is a summary of the standard errors for each sample size:

  ```{r}
plot(
  power_db_eff,
  type = "power"
)

plot(
  power_db_eff,
  type = "se"
)
```

# Compare designs

```{r}
plot_compare_power(
  Random = power_rand,
  Modfed = power_db_eff,
  type = "power"
)

plot_compare_power(
  Random = power_rand,
  Modfed = power_db_eff,
  type = "se"
)
```
