---
title: "Power Analysis"
format: html
theme: united
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.path = "figs/",
    fig.width = 7.252,
    fig.height = 4,
    comment = "#>",
    fig.retina = 3
)

library(tidyverse)
library(cbcTools)
```

First, define the attributes and levels:

```{r}
profiles <- cbc_profiles(
    type = c("Implantable", "Ring", "Bracelet", "Card"),
    price = c(25, 50, 100),
    compatibility = c("iOS", "Android", "iOS/Android"),
    capacity = c(1,3,5), #No of cards
    range = c(0.1,0.5,1) #feet
)
```

# Random design

Make a randomized full-factorial design:

```{r}
design_rand <- cbc_design(
  profiles = profiles,
  n_resp   = 200, # Number of respondents
  n_alts   = 3,   # Number of alternatives per question
  n_q      = 6    # Number of questions per respondent
)

head(design_rand)

cbc_inspect(design_rand)
```

Simulate random choices

```{r}
priors = cbc_priors(
    profiles,
    type       = c(1,1,2),
    price = -0.1,
    compatibility   = c(-1,1),
    capacity  = 1,
    range     = 1
)

choices_rand <- cbc_choices(
    design = design_rand,
    priors = priors
)
```

Run power analysis

```{r}
power_rand <- cbc_power(
    data = choices_rand,
    outcome = "choice",
    obsID = "obsID",
    n_q = 6,
    n_breaks = 10,
    pars    = c("type", "price", "compatibility", "capacity", "range")
)

power_rand
```

Here is a summary of the standard errors for each sample size:

```{r}
plot(
  power_rand,
  type = "power"
)

plot(
  power_rand,
  type = "se"
)
```



# Bayesian D-efficient design

Make a Bayesian D-efficient fractional factorial design:

```{r}
priors = cbc_priors(
    profiles,
    type       = c(1,1,2),
    price = -0.1,
    compatibility   = c(-1,1),
    capacity  = 1,
    range     = 1
)

design_db_eff <- cbc_design(
  profiles  = profiles,
  n_resp    = 200, # Number of respondents
  n_alts    = 3,   # Number of alternatives per question
  n_q       = 6,   # Number of questions per respondent
  n_start   = 10, 
  n_blocks  = 1,
  priors = priors, 
  method = 'modfed'
)

cbc_inspect(design_db_eff)
```

Simulate choices

```{r}
choices_db_eff <- cbc_choices(
    design = design_db_eff,
    priors = priors
)
```

Run power analysis

```{r}
power_db_eff <- cbc_power(
    data = choices_db_eff,
    outcome = "choice",
    obsID = "obsID",
    n_q = 6,
    n_breaks = 10,
    pars    = c("type", "price", "compatibility", "capacity", "range")
)

power_db_eff
```

Here is a summary of the standard errors for each sample size:

```{r}
plot(
  power_db_eff,
  type = "power"
)

plot(
  power_db_eff,
  type = "se"
)
```

# Compare designs

```{r}
plot_compare_power(
  Random = power_rand,
  Modfed = power_db_eff,
  type = "power"
)

plot_compare_power(
  Random = power_rand,
  Modfed = power_db_eff,
  type = "se"
)
```
