---
# General Settings
format: html
echo: false
warning: false

# Theme Settings
theme: default
barposition: top
footer-left: "Made with [surveydown](https://surveydown.org)"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/template_conjoint_buttons)'

# Survey Settings
use-cookies: false
auto-scroll: false
rate-survey: false
system-language: en
highlight-unanswered: true
highlight-color: blue
capture-metadata: true
all-questions-required: true
---

```{r}
library(surveydown)
```

::: {.sd_page id=welcome}
# RFIDInMe Exploring the field of RFID devices

This survey asks about your preferences for **RFID technologies** used for payment and identification — such as **rings**, **bracelets**, **cards**, or **implants**.

```{r}
sd_next()
```
:::

::: {.sd_page id=consent}
# Consent

This survey is being conducted by students at The George Washington University. We will not be collecting any identifying data, such as your name or address. The survey will take about 5 minutes. Your participation is voluntary and you may stop at any time.

```{r}
sd_question(
  type  = 'mc',
  id    = 'consent_age',
  label = "I am age 18 or older",
  option = c('Yes' = 'yes','No' = 'no')
)
```

```{r}
sd_question(
  type  = 'mc',
  id    = 'consent_understand',
  label = "I have read and understand the above information",
  option = c('Yes' = 'yes','No' = 'no')
)
```

```{r}
sd_next()
```

:::

::: {.sd_page id=RFID_Familiarity}
# RFID Familiarity

```{r}
sd_question(
  type  = 'mc',
  id    = 'rfid_familiar',
  label = "Are you familiar with RFID (Radio Frequency Identification) technology?",
  option = c('Yes' = 'yes','No' = 'no')
)
```

```{r}
sd_next()
```

:::

::: {.sd_page id=rfid_info}
# What is RFID Technology?

**RFID (Radio Frequency Identification)** is a wireless technology that uses electromagnetic fields to automatically identify and track tags attached to objects, animals, or people.

## How RFID Works
- **RFID tags** contain electronically stored information
- **RFID readers** can capture data from tags without requiring direct contact or line-of-sight scanning
- Communication happens through **radio waves** at various frequencies

## Common RFID Applications You May Already Use
- **Contactless payment cards** (tap-to-pay credit/debit cards)
- **Key fobs** for building or vehicle access
- **Transit cards** for public transportation
- **Pet microchips** for identification

## RFID vs. Similar Technologies
- **Unlike barcodes**: No line-of-sight required
- **Unlike NFC**: Can work at longer distances (up to several feet)
- **Unlike Bluetooth**: No pairing or active connection needed

## Benefits of RFID
- **Convenience**: Quick, contactless transactions
- **Security**: Encrypted data transmission
- **Durability**: Works through materials like fabric or plastic
- **Speed**: Near-instantaneous data transfer

Now that you understand RFID technology, let's continue with the survey!

```{r}
sd_next()
```

:::

::: {.sd_page id=screening}
# Screening Question

If you are **interested in alternatives to carrying a wallet** (for payments or ID) using RFID technology, please select **Interested**.\
If you are **not interested at all**, select **Not interested**.

```{r}
sd_question(
  type  = 'mc',
  id    = 'screenout',
  label = "Overall, how interested are you in using RFID for payments or identification?",
  option = c('Not interested' = 'blue', 'Interested' = 'red')
)
```

```{r}
sd_next()
```

:::

::: {.sd_page id=needles_page}
# Grouping Question

```{r}
sd_question(
  type  = 'mc',
  id    = 'needles',
  label = "Are you afraid of needles?",
  option = c('Yes' = 'blue', 'No' = 'red')
)
```

```{r}
sd_next()
```

:::

::: {.sd_page id=educational}
# Educational Page

Now that you've shared a bit about yourself, consider a scenario in which you can choose an **RFID technology** from a set of options with different attributes.

## Price

The cost (USD) you would pay for the device.

## Range

How far (in feet) a scanner can detect the RFID signal (e.g., 0.1, 0.5, or 1 ft).

## Compatibility

Which phone ecosystem the device pairs with: **iOS**, **Android**, or **Both**.

## Storage

How many digital ID tags can be stored (e.g., **1**, **3**, or **5 Tags**).

## Type / Location

We will show several **form factors**: - **Bracelet** or **Ring** (wearables) - **Card** (wallet alternative) - **Implant** (subdermal location such as **hand**, **wrist**, or **finger**)

```{r}
sd_next()
```
:::

::: {.sd_page id=cbc_intro}
# Conjoint Question Intro

On the next pages, you'll see three RFID options. Choose the one you most prefer.

We will now show you 6 sets of choice questions starting on the next page.

```{r}
sd_next()
```
:::

::: {.sd_page id=cbc_q1_page}
# Conjoint Question 1

```{r}
sd_output("cbc_q1", type = "question")
```

```{r}
sd_next()
```

:::

::: {.sd_page id=cbc_q2_page}
# Conjoint Question 2

```{r}
sd_output("cbc_q2", type = "question")
```

```{r}
sd_next()
```

:::

::: {.sd_page id=cbc_q3_page}
# Conjoint Question 3

```{r}
sd_output("cbc_q3", type = "question")
```

```{r}
sd_next()
```

:::

::: {.sd_page id=cbc_q4_page}
# Conjoint Question 4

```{r}
sd_output("cbc_q4", type = "question")
```

```{r}
sd_next()
```

:::

::: {.sd_page id=cbc_q5_page}
# Conjoint Question 5

```{r}
sd_output("cbc_q5", type = "question")
```

```{r}
sd_next()
```

:::

::: {.sd_page id=cbc_q6_page}
# Conjoint Question 6

```{r}
sd_output("cbc_q6", type = "question")
```

```{r}
sd_next()
```

:::

::: {.sd_page id=demographics}
# Demographics Page

## Nice job!

We're almost done! We'd just like to ask just a few more questions about you which we will only use for analyzing our survey data.

::: {style="width:500px; margin: 0 auto;"}
```{r}
year_options <- setNames(as.character(1980:2015), as.character(1980:2015))

sd_question(
  type   = 'select',
  id     = 'year_of_birth',
  label  = "(1) In what year were you born?",
  option = year_options
)
```

```{r}
genders <- c("Man" = "man", "Woman" = "woman", "Non-binary" = "nonbinary", "Other" = "other", "Prefer Not to Answer" = "prefer_not_to_answer")

sd_question(
  type   = 'select',
  id     = 'gender',
  label  = "(2) What is your current gender identity?",
  option = genders
)
```

```{r}
sd_question(
  type  = "textarea",
  id    = "feedback",
  label = 
  "Please let us know if you have any other thoughts or feedback on this survey.
  
  Your feedback will help us make future improvements :)"
)
```

```{r}
sd_next()
```

:::
:::

::: {.sd_page id=end_normal}
# End Page

The survey is finished. Thank you for your feedback!

Your completion code is: **`r sd_output('completion_code', type = 'value')`**

You may close the window now.

```{r}
sd_close()
```
:::

::: {.sd_page id=end_consent}
# End Page

The survey is now finished. You may close the window.

```{r}
sd_close()
```
:::

::: {.sd_page id=end_screenout}
# End Page

Sorry, we wanted you to select the **red** button.

The survey is now finished. You may close the window.

```{r}
sd_close()
```
:::
