---
# General Settings
format: html
echo: false
warning: false

# Theme Settings
theme: default
barposition: top
footer-left: "Made with [surveydown](https://surveydown.org)"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/template_conjoint_buttons)'

# Survey Settings
use-cookies: false
auto-scroll: false
rate-survey: false
system-language: en
highlight-unanswered: true
highlight-color: blue
capture-metadata: true
all-questions-required: true
---

```{r}
library(surveydown)
```

::: {#welcome .sd_page}
This survey asks about your preferences for **RFID technologies** used for payment and identification — such as **rings**, **bracelets**, **cards**, or **implants**.

```{r}
sd_next()
```
:::

::: {#consent .sd_page}
# Consent

This survey is being conducted by students at The George Washington University. We will not be collecting any identifying data, such as your name or address. The survey will take about 10–15 minutes. Your participation is voluntary and you may stop at any time.

```{r}
sd_question(
  type  = 'mc',
  id    = 'consent_age',
  label = "I am age 18 or older",
  option = c('Yes' = 'yes','No' = 'no')
)

sd_question(
  type  = 'mc',
  id    = 'consent_understand',
  label = "I have read and understand the above information",
  option = c('Yes' = 'yes','No' = 'no')
)

sd_next()
```
:::

::: {#favorite_fruit .sd_page}
# RFID Familiarity

```{r}
sd_question(
  type  = 'mc',
  id    = 'rfid_interest',
  label = "Are you familiar with RFID technology?",
  option = c('Yes!' = 'yes','Kind of' = 'kind_of','No :(' = 'no')
)

sd_next()
```
:::

::: {#screening .sd_page}
# Screening Question

If you are **interested in alternatives to carrying a wallet** (for payments or ID) using RFID technology, please select **Interested**.\
If you are **not interested at all**, select **Not interested**.

```{r}
sd_question(
  type  = 'mc',
  id    = 'screenout',
  label = "Overall, how interested are you in using RFID for payments or identification?",
  option = c('Not interested' = 'blue', 'Interested' = 'red')
)

sd_next()
```
:::

::: {#educational .sd_page}
# Educational Page

Now that you've shared a bit about yourself, consider a scenario in which you can choose an **RFID technology** from a set of options with different attributes.

## Price

The cost (USD) you would pay for the device.

## Range

How far (in feet) a scanner can detect the RFID signal (e.g., 0.1, 0.5, or 1 ft).

## Compatibility

Which phone ecosystem the device pairs with: **iOS**, **Android**, or **Both**.

## Storage

How many digital ID tags can be stored (e.g., **1**, **3**, or **5 Tags**).

## Type / Location

We will show several **form factors**: - **Bracelet** or **Ring** (wearables) - **Card** (wallet alternative) - **Implant** (subdermal location such as **hand**, **wrist**, or **finger**)

```{r}
sd_next()
```
:::

::: {#cbc_intro .sd_page}
# Conjoint Question Intro

On the next pages, you’ll see three RFID options. Choose the one you most prefer.

We will now show you 6 sets of choice questions starting on the next page.

```{r}
sd_next()
```
:::

::: {#cbc_q1_page .sd_page}
# Conjoint Question 1

```{r}
sd_output("cbc_q1", type = "question")
sd_next()
```
:::

::: {#cbc_q2_page .sd_page}
# Conjoint Question 2

```{r}
sd_output("cbc_q2", type = "question")
sd_next()
```
:::

::: {#cbc_q3_page .sd_page}
# Conjoint Question 3

```{r}
sd_output("cbc_q3", type = "question")
sd_next()
```
:::

::: {#cbc_q4_page .sd_page}
# Conjoint Question 4

```{r}
sd_output("cbc_q4", type = "question")
sd_next()
```
:::

::: {#cbc_q5_page .sd_page}
# Conjoint Question 5

```{r}
sd_output("cbc_q5", type = "question")
sd_next()
```
:::

::: {#cbc_q6_page .sd_page}
# Conjoint Question 6

```{r}
sd_output("cbc_q6", type = "question")
sd_next()
```
:::

::: {#demographics .sd_page}
# Demographics Page

## Nice job!

We're almost done! We'd just like to ask just a few more questions about you which we will only use for analyzing our survey data.

::: {style="width:500px; margin: 0 auto;"}
```{r}
# Construct the list of years

years <- as.character(2003:1920)
names(years) <- years
years <- c("Prefer not to say" = "prefer_not_say", years)

sd_question(
  type   = 'select',
  id     = 'year_of_birth',
  label  = "(1) In what year were you born?",
  option = years
)

genders <- c(
  "Male"                     = "male",
  "Female"                   = "female", 
  "Non-binary"               = "non_binary", 
  "Trans male/trans man"     = "trans_male",
  "Trans female/trans woman" = "trans_female",
  "Prefer not to say"        = "prefer_not_to_say"
)

sd_question(
  type   = 'select',
  id     = 'gender',
  label  = "(2) What is your current gender identity?",
  option = genders
)

sd_question(
  type  = "textarea",
  id    = "feedback",
  label = 
  "Please let us know if you have any other thoughts or feedback on this survey.
  
  Your feedback will help us make future improvements :)"
)

sd_next()
```
:::
:::

::: {#end_normal .sd_page}
# End Page

The survey is finished. Thank you for your feedback!

Your completion code is: **`r sd_output('completion_code', type = 'value')`**

You may close the window now.

```{r}
sd_close()
```
:::

::: {#end_consent .sd_page}
# End Page

The survey is now finished. You may close the window.

```{r}
sd_close()
```
:::

::: {#end_screenout .sd_page}
# End Page

Sorry, we wanted you to select the **red** button.

The survey is now finished. You may close the window.

```{r}
sd_close()
```
:::
